Exploring mathematical objects from custom-tailored mathematical universes

### 2018-05-30 slides-filmat2018.tex
typo
Slides in the version they went live

      \item \intex{
        $\Sh(X) \models \text{``Any cont. function with opposite signs has
        a zero.''}$
      }{\textcolor{red!80}{\xmark}}{
        Meaning: Zeros can locally be picked \hil{continuously} in
        continuous families of continuous functions.
        \textcolor{red}{(\href{https://rawgit.com/iblech/internal-methods/master/images/zeros-in-families.mp4}{video} for counterexample)}
      }
    \end{itemize}
  \end{changemargin}
\end{frame}

@@

\section{Conclusion}

\begin{frame}{Topos theory \ldots}
  \vspace*{-0.5em}
  \begin{itemize}
    \item enriches the platonism debate,
    %\item yields a new view on ``continuous dependence on parameters'',
    \item uncovers further relations between objects,
    \item allows to view objects from a different point of view,
    \item has applications in mathematical practice.
  \end{itemize}

>>>>

      \item \intex{
        $\Sh(X) \models \text{``Any cont. function with opposite signs has
        a zero.''}$
      }{\textcolor{red!80}{\xmark}}{
        Meaning: Zeros can locally be picked \hil{continuously} in
        continuous families of continuous functions.
        \textcolor{red!80}{(\href{https://rawgit.com/iblech/internal-methods/master/images/zeros-in-families.mp4}{video} for counterexample)}
      }
    \end{itemize}
  \end{changemargin}
\end{frame}

@@

\appendix
\section{Conclusion}

\begin{frame}{Topos theory \ldots}
  \vspace*{-0.5em}
  \begin{itemize}
    \item enriches the platonism debate,
    %\item yields a new view on ``continuous dependence on parameters'',
    \item uncovers further relations between objects,
    \item allows to study objects from a different point of view,
    \item has applications in mathematical practice.
  \end{itemize}
